Investigating Determinism of Gaming Engines for Autonomous Vehicle Verification

### 2020-03-06 paper/6_Conclusions.tex

\section{Conclusions}\label{s:conclusion}
We have provided a summary of the sources of non-determinisim in game engines. This was followed by presenting a method by which one can determine the simulation variance of a gaming engine used in V\&V application of CAV simulations. The method consists of five stages, starting with designing the experiment, then suggesting the various settings that can improve or worsen the performance, and finally focuses on running the experiment and analysing the output.

>>>>

\section{Conclusions}\label{s:conclusion}

\todo{KIE: Mention our ResiCAV experiments and the importance to recognize that once physics is involved then a single experiment is not sufficient to determine the outcome / impact of a test. Instead, at this stage several thousands of tests may need to be executed to obtain reliable statistics to estimate the worst/best case.}

We have provided a summary of the sources of non-determinisim in game engines. This was followed by presenting a method by which one can determine the simulation variance of a gaming engine used in V\&V application of CAV simulations. The method consists of five stages, starting with designing the experiment, then suggesting the various settings that can improve or worsen the performance, and finally focuses on running the experiment and analysing the output.
